Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v1.0)} \underline{Drafting Committee: DC90 (\today)}

### 2011-04-01 background_and_systematic.tex
Removed blue text

Another contribution to the systematic uncertainty comes from the relative shift of the
missing-mass distributions. \blue{There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}}. \blue{The missing-mass
distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for the observed time dependence.} One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty. The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation because it describes the data well and is consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. 
\blue{The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
which has been eliminated for the 2006-2007 data sample.}
These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

The data sample in the exclusive region contains events involving both
production of real photons in which the proton remains intact and
events involving the excitation of the target proton to a $\Delta^+$
resonant state. \blue{The} recoiling proton is not detected \blue{and
  the calorimeter resolution does not allow} separation of the latter events from rest of the data sample.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform \blue{this} estimation is described in detail in
Ref.~\cite{Air08}.

\begin{table}
 \begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the systematic uncertainty due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data to the total
systematic uncertainty. The total systematic uncertainties, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

>>>>

Another contribution to the systematic uncertainty comes from the relative shift of the
missing-mass distributions. There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}. The missing-mass
distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for the observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty. The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation because it describes the data well and is consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. 
The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
which has been eliminated for the 2006-2007 data sample.
These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

The data sample in the exclusive region contains events involving both
production of real photons in which the proton remains intact and
events involving the excitation of the target proton to a $\Delta^+$
resonant state. The recoiling proton is not detected and
  the calorimeter resolution does not allow separation of the latter events from rest of the data sample.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation from Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform this estimation is described in detail in
Ref.~\cite{Air08}.

\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift  & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to the systematic uncertainty due to the
background correction, the time-dependent shifts of the missing-mass
distributions and detector effects for the 2006-2007 data to the total
systematic uncertainty. The total systematic uncertainties, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

### 2011-04-01 experiment_and_data.tex
Added the JHEP style
Removed blue text

An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$ of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter. Here, $q$ is the four-momentum of the virtual photon, $\blue{P}$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\blue{\textrm{UU}}}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where $\mathcal{L}$ is the integrated luminosity, $\eta$ \blue{is} the detection
efficiency and d$\sigma_{\blue{\textrm{UU}}}$ denotes the
cross section for an unpolarised target integrated over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,DVCS}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite Fourier series
caused by the azimuthal dependencies in the denominators from
Eqs.~\ref{e:alui}-\ref{e:ac}. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
are included as both a consistency check for extraneous harmonics caused
by the denominators in Eqs.~\ref{e:alui}-\ref{e:ac} and as a test of the
normalisation of the fit. These terms are expected to be small.

@@

At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes\blue{,} for an unpolarised target\blue{,} are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), to first approximation the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, in this approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. Using this dependence, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
\blue{where $\alpha_{\textrm{S}}$ is the fine structue constant}.
\begin{table}[H]
\begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Relative Suppression \\
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& --
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} calorimeter. Here, $q$ is the four-momentum of the virtual photon, $p$ is the initial four-momentum of the target proton and $q'$ is the four-momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.

@@

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\textrm{UU}}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
efficiency and d$\sigma_{\textrm{UU}}$ denotes the
cross section for an unpolarised target integrated over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
\label{alui_asym}
\end{equation}
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,DVCS}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite Fourier series
caused by the azimuthal dependencies in the denominators from
Eqs.~\ref{e:alui}-\ref{e:ac}. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
are included as both a consistency check for extraneous harmonics caused
by the denominators in Eqs.~\ref{e:alui}-\ref{e:ac} and as a test of the
normalisation of the fit. These terms are expected to be small.

@@

At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), to first approximation the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, in this approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. Using this dependence, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the fine structue constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& --
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2011-04-01 frame.tex
Removed blue text

\begin{document}
\title{Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.9)}
        \underline{Drafting Committee: DC90 (\today)}
}

@@

\abstract{
Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from \blue{the} earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from \blue{the two} data sets are found to be compatible with each other. Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
}
\keywords{lepton-nucleon scattering}

>>>>

\begin{document}
\title{Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS0607 (v1.0)}
        \underline{Drafting Committee: DC90 (\today)}
}

@@

\abstract{
Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the H{\sc ermes} data set of 2006-2007 using a missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from the earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from the two data sets are found to be compatible with each other. Combined results from these data sets are extracted and represent the statistically most precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
}
\keywords{lepton-nucleon scattering}
